\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[margin=2.5cm]{geometry}
\usepackage{natbib}
\usepackage{authblk}

\title{LitScribe: A Multi-Agent Literature Review Engine with \\Citation Grounding and Contradiction-Aware Synthesis}

\author[1]{Arnold Zhou}
\affil[1]{Independent Researcher}

\date{May 2026}

\begin{document}

\maketitle

\begin{abstract}
We present LitScribe, an open-source multi-agent system that generates comprehensive academic literature reviews from natural language research questions. Unlike existing tools that either generate unverified reviews or detect contradictions without producing reviews, LitScribe combines both capabilities in an end-to-end pipeline. The system searches up to six academic databases, analyzes papers with full-text support via Unpaywall, and generates reviews with Pandoc-style citations individually verified against source papers (62--100\% grounding accuracy, 75\% average). We introduce three novel capabilities: (1)~contradiction-aware synthesis, which detects opposing findings between papers and weaves them into the review narrative; (2)~metacognitive quality loops, where the system evaluates its own output and autonomously decides which pipeline steps to re-run; and (3)~search-augmented refinement, where user requests to add content trigger new paper searches before writing. Evaluation on five queries across four domains (Biology, Computer Science, Medicine, Chemistry) shows the system produces 1,300--1,750 word reviews with 0.55--0.82 quality scores in approximately two minutes. LitScribe is available at \url{https://github.com/arnold117/LitScribe} under the MIT license.
\end{abstract}

\section{Introduction}

Literature reviews are foundational to scientific progress, yet they remain one of the most time-consuming tasks in academic research. A comprehensive review requires searching multiple databases, reading dozens of papers, identifying themes and contradictions, synthesizing findings, and properly citing sources. Recent advances in large language models (LLMs) have prompted several attempts to automate this process, but existing approaches suffer from three critical limitations.

First, most LLM-based review tools rely on the model's training data rather than searching academic databases, leading to outdated or fabricated references. Second, tools that do search databases typically generate reviews without verifying whether their citations actually support the claims being made---a problem that leads to citation hallucination rates of 15--20\% even in state-of-the-art models \citep{hallucination2026}. Third, no existing system automatically identifies contradictions between papers and presents them as part of the review narrative.

LitScribe addresses these limitations through a deterministic pipeline built on the DeepAgents framework \citep{deepagents2025}. Given a research question, the system:
\begin{enumerate}[nosep]
    \item[\textbf{1--2.}] Decomposes the question into sub-topics and searches up to six academic databases in parallel;
    \item[\textbf{3--4.}] Enriches papers with open-access full text via Unpaywall, then analyzes each paper for key findings;
    \item[\textbf{5--6.}] Detects contradictions between papers and builds a knowledge graph (GraphRAG);
    \item[\textbf{7--8.}] Generates review sections in parallel and conducts a multi-agent debate (reviewer vs.\ synthesizer);
    \item[\textbf{9--10.}] Verifies every citation against its source paper, then self-evaluates quality with loop-back;
    \item[\textbf{11.}] Applies metacognitive evaluation and saves results to a persistent knowledge base.
\end{enumerate}

Our contributions are:
\begin{enumerate}[nosep]
    \item \textbf{Contradiction-aware synthesis}: The first system to detect contradictions between papers and integrate them into the generated review as critical analysis.
    \item \textbf{Metacognitive quality loops}: The system evaluates its own output across multiple dimensions and autonomously decides which pipeline steps to re-run with adjusted strategies.
    \item \textbf{Search-augmented refinement}: When users request new content, the system searches for relevant papers before writing, preventing hallucination in iterative review modification.
\end{enumerate}

\section{Related Work}

\subsection{Automated Survey Generation}

Several systems have been proposed for automated literature review generation. SurveyG \citep{surveyg2025} uses a hierarchical citation graph with foundation/development/frontier layers to organize papers temporally. InteractiveSurvey \citep{interactivesurvey2025} allows users to customize intermediate components during generation. LLM $\times$ MapReduce-V3 \citep{llmmapreduce2025} uses MCP-driven modular agents for survey generation. AutoResearchClaw \citep{autoresearchclaw2025} implements a 23-stage pipeline covering ideation through paper writing. However, none of these systems verify their citations against source papers or detect contradictions between papers.

\subsection{Citation Verification}

PaperQA2 \citep{paperqa2025} achieves superhuman performance on scientific question answering with citations and includes a contradiction detection agent that evaluates claims against the literature. However, PaperQA2 is a question-answering system, not a review generator. The REFIND framework \citep{refind2025} detects span-level hallucinations using context sensitivity ratios but does not generate reviews. Scite.ai classifies citations as supporting or contrasting but does not synthesize reviews.

\subsection{Our Position}

LitScribe occupies a unique position: it is the first system to combine multi-source academic search, full review generation, citation grounding, and contradiction detection in a single end-to-end pipeline. Table~\ref{tab:comparison} summarizes the comparison.

\begin{table}[h]
\centering
\caption{Feature comparison with existing tools.}
\label{tab:comparison}
\small
\begin{tabular}{lccccc}
\toprule
Capability & LitScribe & ChatGPT & PaperQA2 & SurveyG & Elicit \\
\midrule
Multi-source search (6 DBs) & \checkmark & -- & -- & -- & \checkmark \\
Full review generation & \checkmark & \checkmark & -- & \checkmark & -- \\
Citation grounding & \checkmark & -- & \checkmark & -- & -- \\
Contradiction detection & \checkmark & -- & \checkmark & -- & -- \\
Multi-agent debate & \checkmark & -- & -- & -- & -- \\
Metacognitive loop & \checkmark & -- & -- & -- & -- \\
Cross-lingual (EN+ZH) & \checkmark & \checkmark & -- & -- & -- \\
Local paper modes & \checkmark & -- & -- & -- & -- \\
\bottomrule
\end{tabular}
\end{table}

\section{System Architecture}

\subsection{Overview}

LitScribe is built on the DeepAgents framework, which provides a supervisor agent that interprets user intent through natural language and dispatches to appropriate tools. The core review pipeline is implemented as a deterministic function rather than LLM-driven routing, ensuring reproducibility and predictable execution time.

The system comprises 86 Python source files (10,300 lines of code in the \texttt{litscribe/} package), with 49 unit tests, 12 CLI commands, 16 REST API endpoints, and a web interface with server-sent event (SSE) streaming.

\subsection{Search Layer}

LitScribe searches up to six academic databases in parallel: OpenAlex (250M+ works), Europe PMC (40M+, including bioRxiv/medRxiv preprints), PubMed (35M+, when configured with NCBI credentials), Semantic Scholar (200M+), arXiv (2M+), and CrossRef (140M+). Search is domain-aware: arXiv is automatically skipped for biology, medicine, and chemistry queries, as its corpus skews heavily toward computer science and physics, causing keyword-matching false positives in other domains.

After search, papers undergo three filtering stages: (1)~DOI-based deduplication across sources, (2)~keyword relevance filtering requiring at least two core terms from the research question, and (3)~LLM-based selection where the model chooses the most relevant papers from the candidate set. Papers are then enriched with open-access PDF URLs via the Unpaywall API, which provides open-access coverage for approximately 68\% of academic papers with DOIs.

\subsection{Analysis Pipeline}

Each paper is analyzed by the LLM to extract key findings (up to 8), methodology summary, strengths, limitations, and a relevance score. Papers scoring below an adaptive threshold are removed: 0.5 for sets with $>$8 papers, 0.3 for 4--8 papers, and 0.2 for $<$4 papers. This prevents over-filtering in niche domains while maintaining quality in well-covered topics.

\subsection{Contradiction Detection}

Contradictions are detected at two levels:

\textbf{Paper-level}: All pairs of papers (up to 15 pairs) are compared by the LLM, which classifies contradictions as methodological, data inconsistency, or opposing conclusions, with minor/moderate/major severity.

\textbf{Claim-level}: After synthesis, claims in the generated review are extracted and checked for internal contradictions.

Detected contradictions are formatted and injected into the synthesis prompt, resulting in a critical analysis section in the review.

\subsection{Parallel Synthesis}

Reviews are generated using parallel section generation: introduction, theme sections, and conclusion are generated concurrently by separate LLM calls. Each section receives the paper summaries relevant to its theme, along with citation keys and a strict citation rule requiring Pandoc-style \texttt{[@key]} format. The sections are assembled and augmented with a methodology comparison table, research timeline, statistical summary, and figure suggestions---all generated in parallel.

\subsection{Multi-Agent Debate}

After synthesis, a reviewer agent critiques the review, identifying unsupported claims, missing perspectives, logical gaps, and weak synthesis. The synthesizer agent then revises the review to address all identified issues. This process runs for up to 2 rounds and stops when the reviewer assesses quality as ``good'' or ``excellent.''

\subsection{Citation Grounding}

Every \texttt{[@key]} citation in the review is verified against the source paper. The system:
\begin{enumerate}[nosep]
    \item Extracts all citations with their surrounding claims
    \item Maps citation keys to paper IDs
    \item Asks the LLM whether each claim is broadly supported by the paper's content
    \item Auto-rewrites unsupported claims
\end{enumerate}

The grounding prompt is deliberately lenient: claims are marked unsupported only if they directly contradict the paper or attribute findings the paper never discussed.

\subsection{Metacognitive Quality Loop}

After the self-review step, a metacognitive evaluator analyzes the review's score, coverage, grounding accuracy, and contradiction count. It then decides which pipeline steps (if any) should be re-run with adjusted strategies. For example, if coverage is low, it may trigger a re-search with refined queries; if coherence is weak, it may trigger re-synthesis. Adjustment strategies are saved to a persistent knowledge base for future reviews in the same domain.

\subsection{Knowledge Base and Session Persistence}

LitScribe maintains a cross-session knowledge base where key findings from each review are stored with HMAC-SHA256 integrity signatures. On subsequent reviews, past findings in the same domain are automatically retrieved and injected as ``Prior Knowledge'' context. Tampered entries (e.g., from database manipulation) are detected via signature verification and silently rejected.

\section{Evaluation}

\subsection{Benchmark Setup}

We evaluate LitScribe on five queries spanning four academic domains (Biology, Computer Science, Medicine, Chemistry), using up to 12 papers per query. The LLM backend is DeepSeek V4 Flash via the DeepSeek API. Each query runs through the core pipeline (plan, search, read, contradictions, synthesize, ground, review) without the optional appendix generation (comparison table, timeline, statistics, figure suggestions) to reduce API calls and isolate core review quality.

\subsection{Results}

\begin{table}[h]
\centering
\caption{Benchmark results across five domains.}
\label{tab:benchmark}
\begin{tabular}{llccccc}
\toprule
Label & Domain & Papers & Words & Score & Grounding & Time \\
\midrule
BIO-1 & Biology & 9 & 1,649 & \textbf{0.82} & 83\% & 106s \\
CS-2 & Computer Science & 12 & 1,535 & 0.72 & 63\% & 121s \\
MED-1 & Medicine & 12 & 1,709 & 0.65 & 68\% & 115s \\
CS-1 & Computer Science & 12 & 1,643 & 0.55 & 62\% & 153s \\
CHEM-1 & Chemistry & 3 & 1,338 & 0.55 & 100\% & 103s \\
\midrule
\multicolumn{2}{l}{\textit{Average}} & 9.6 & 1,575 & 0.66 & 75\% & 120s \\
\bottomrule
\end{tabular}
\end{table}

Biology achieves the highest score (0.82), benefiting from strong coverage in PubMed and Europe PMC. Chemistry scores lower (0.55) due to the niche nature of the query (sesquiterpene coumarin biosynthesis), which returns only 3 relevant papers after filtering. Computer Science scores are affected by arXiv rate-limiting (HTTP 429), which reduces the paper pool quality for CS-specific topics.

\subsection{Grounding Accuracy}

Citation grounding accuracy ranges from 62\% to 100\%, with an average of 75\%. The highest accuracy (100\%) is achieved on the Chemistry query, where only 3 highly relevant papers are used, resulting in precise citations. Lower accuracy on CS queries (62--63\%) is attributed to heavier paraphrasing of technical findings during synthesis.

\subsection{Limitations}

The current evaluation relies on LLM self-review scores, which may not correlate perfectly with human judgments. Future work will include human evaluation with domain experts and baseline comparisons against ChatGPT and Elicit. Additionally, arXiv rate-limiting affects CS domain performance, and the system does not yet search Chinese-language databases (CNKI, Wanfang) despite supporting Chinese review generation.

\section{Conclusion}

We presented LitScribe, a multi-agent literature review engine that introduces three novel capabilities: contradiction-aware synthesis, metacognitive quality loops, and search-augmented refinement. The system generates comprehensive reviews from natural language queries in approximately two minutes, with citations verified against source papers. LitScribe is open-source under the MIT license and available at \url{https://github.com/arnold117/LitScribe}.

Future directions include human evaluation, baseline comparisons, social media academic trend monitoring (WeChat Official Accounts, Twitter), related work section generation for paper writing, and a React-based web interface with rich text editing.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
